Body Mass index effects on statin prescribtions

### 2020-11-16 manuscript/manuscript.Rmd
update

---
title: "BMI-manuscript"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}
Body Mass Idex (BMI) playes an important rule in predicting heart disease risk. BMI     
 .
[@van2012estimating]
\section{methode}
From the figure we see ...

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory.png"))) {
    source(here::here("exploratory-data-analysis.R"))
}
knitr::include_graphics(here::here("images", "exploratory.png"))
```
# References

>>>>

---
title: "Body Mass index effects on statin prescribtions"
output: 
    bookdown::pdf_document2:  
        keep_tex: true
bibliography: cite.bib
link_citations: true
---
\section{introduction}

Body Mass Index (BMI) plays an important rule in predicting heart disease risk[@katbody]. Our goal is to compare 90Th quantile regression for BMI in Diabetes and prediabetes population. Quantile regression has many succesfyl application in ecology where different factores interect in a complicated way that produce different variation of one factor for different levels of another variabels[@cade2003].

\section{Quantile Regression}
Quantile regression is an important tool used to regress the dependent variable with high variance over the independent variables. QR is developed to study the relationships between variables that have week or no-relationshipes between their means. Quantile regression is more robust for an  outlier than ordinaty least squares regression(OLS). Moreover, QR is  . The independent variables are Gender, Age, race, diabetes status, and statin use.

For a random variable $X$, the cumulative distrubution function (CDF) is $$F(X)=P(X\leq x)$$, and the $\tau$th quantile of $X$ is defined by $$ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} $$ where $0<\tau<1$.
Let the loss function is defined by $$\rho_{\tau}(u)= u(\tau-I_{(u<0)})$$ where $I$ is the indicator function  [@koenker2005]. The quantile estimator is the value that manimizes the expected loss function

$E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).$
Differentiating with respect to $\hat{x}$, we get
$$ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
=F(\hat{x})-\tau.$$ 
Due to monotnicity of the cumulative distribution function, any solution that satisfies $\{x:F(x)=\tau \}$ is a minimzing for the expected loss function.

Least square method expresses conditional mean of y given x as $\mu(x)=x^T\beta$ and it solves $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.$$ Quantile regression expresses conditional quantile function $Q_y(\tau|x)=x^T \beta ({\tau)}$ and solve $$ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.$$This minimization problem can be reformalated to a linear programming problem $$ \underset{\beta\in \mathcal{R}^p}{\text{min}} $$

\section{methods}

prevalence and incidence as a function
of age (18 – 84 years in 1-year
intervals), race/ethnicity (non-Hispanic
white, non-Hispanic black, Hispanic, or
other), sex, and BMI (underweight,
 18.5 kg/m2; normal weight, 18.5 to
 25 kg/m2; overweight, 25 to 30 kg/
m2; obese, 30 to 35 kg/m2; and very
From the figure we see

#Data
 The data used in this study is National Health and Nutrition Examination Survey data (NHANES)[@NHANES]. The data has

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory.png"))) {
    source(here::here("exploratory-data-analysis.R"))
}
knitr::include_graphics(here::here("images", "exploratory.png"))
```

However,.

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "exploratory2.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "exploratory2.png"))
```

So,

```{r, out.width = "80%", fig.align = "center", fig.cap = "A better figure caption", echo = FALSE}
# Created by file exploratory-data-analysis.R
if (!file.exists(here::here("images", "quant90.png"))) {
    source(here::here("exploratory-data-analysis_JRT.R"))
}
knitr::include_graphics(here::here("images", "quant90.png"))
```
# References

### 2020-11-16 manuscript/manuscript.tex
update

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={BMI-manuscript},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{BMI-manuscript}
\author{}
\date{\vspace{-2.5em}}

@@

Body Mass Index (BMI) plays an important rule in predicting heart
disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90th
quatile regrission for BMI in Diabtese and prediabtes population.

(Van de Kassteele et al. 2012)

@@

\section{Quantile regression}

Quantile regression is an important tool used to regress the dependent
variable with high variance over the independent variables.

For a random variable \(X\), the comulative distrubution function (CDF)
is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\)

@@

The data used in this study is National Health and Nutrition Examination
Survey data (NHANES)(Disease Control and (CDC) 2018)

@@

@@

\hypertarget{refs}{}
\hypertarget{ref-NHANES}{}
Disease Control, Centers for, and Prevention (CDC). 2018. ``National
Health and Nutrition Examination Survey Data (Nhanes.''

@@

\hypertarget{ref-van2012estimating}{}
Van de Kassteele, Jan, RT Hoogenveen, PM Engelfriet, PHM Van Baal, and
HC Boshuizen. 2012. ``Estimating Net Transition Probabilities from
Cross-Sectional Data with Application to Risk Factors in Chronic Disease
Modeling.'' \emph{Statistics in Medicine} 31 (6). Wiley Online Library:
533--43.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Body Mass index effects on statin prescribtions},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Body Mass index effects on statin prescribtions}
\author{}
\date{\vspace{-2.5em}}

@@

Body Mass Index (BMI) plays an important rule in predicting heart
disease risk(Katzmarzyk et al. 2012). Our goal is to compare 90Th
quantile regression for BMI in Diabetes and prediabetes population.
Quantile regression has many succesfyl application in ecology where
different factores interect in a complicated way that produce different
variation of one factor for different levels of another variabels(Cade
and Noon 2003).

\section{Quantile Regression}

Quantile regression is an important tool used to regress the dependent
variable with high variance over the independent variables. QR is
developed to study the relationships between variables that have week or
no-relationshipes between their means. Quantile regression is more
robust for an outlier than ordinaty least squares regression(OLS).
Moreover, QR is . The independent variables are Gender, Age, race,
diabetes status, and statin use.

For a random variable \(X\), the cumulative distrubution function (CDF)
is \[F(X)=P(X\leq x)\], and the \(\tau\)th quantile of \(X\) is defined
by \[ F^{-1}(\tau)=\text{inf}\{x: F(x)\ge \tau\} \] where \(0<\tau<1\).
Let the loss function is defined by
\[\rho_{\tau}(u)= u(\tau-I_{(u<0)})\] where \(I\) is the indicator
function (Koenker 2005). The quantile estimator is the value that
manimizes the expected loss function

\(E\rho_{\tau}(X-\hat{x})=(\tau-1)\int_{-\infty}^{\hat{x}} (x-\hat{x})dF(x)+\tau\int_{\hat{x}}^{-\infty} (x-\hat{x})dF(x).\)
Differentiating with respect to \(\hat{x}\), we get
\[ 0  =(\tau-1)\int_{-\infty}^{\hat{x}} dF(x)+\tau\int_{\hat{x}}^{-\infty} dF(x)
=F(\hat{x})-\tau.\] Due to monotnicity of the cumulative distribution
function, any solution that satisfies \(\{x:F(x)=\tau \}\) is a
minimzing for the expected loss function.

Least square method expresses conditional mean of y given x as
\(\mu(x)=x^T\beta\) and it solves
\[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n(y_i- x_i^T\beta)^2.\]
Quantile regression expresses conditional quantile function
\(Q_y(\tau|x)=x^T \beta ({\tau)}\) and solve
\[ \underset{\beta\in \mathcal{R}^p}{\text{min}}\sum_{i=1}^n\rho_{\tau}(y_i- x_i^T\beta)^2.\]This
minimization problem can be reformalated to a linear programming problem
\[ \underset{\beta\in \mathcal{R}^p}{\text{min}} \]

@@

@@

The data used in this study is National Health and Nutrition Examination
Survey data (NHANES)(Disease Control and (CDC) 2018). The data has

@@

However,.

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/exploratory2}

\caption{A better figure caption}\label{fig:unnamed-chunk-2}
\end{figure}

So,

{\centering \includegraphics[width=0.8\linewidth]{C:/Users/Muhannad/Desktop/multvariat/R_codes/tonton/BMI/images/quant90}

\caption{A better figure caption}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\hypertarget{refs}{}
\hypertarget{ref-cade2003}{}
Cade, Brian S, and Barry R Noon. 2003. ``A Gentle Introduction to
Quantile Regression for Ecologists.'' \emph{Frontiers in Ecology and the
Environment} 1 (8). Wiley Online Library: 412--20.

\hypertarget{ref-NHANES}{}
Disease Control, Centers for, and Prevention (CDC). 2018. ``National
Health and Nutrition Examination Survey Data (Nhanes.''

@@

\hypertarget{ref-koenker2005}{}
Koenker, Roger. 2005. ``Quantile Regression, Volume 38 of.''
\emph{Econometric Society Monographs}.
